Supplementary Information

### 2021-01-12 doc/manuscript/MEE_manuscript.Rmd
Update MEE_manuscript.Rmd
#108

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Jan6)
n_spst_DBH_analyzed= 43 # n species with DBH analyzed: 43 (45 - 2: 2 Hansley)
n_spst_RW_DBH_sig=35 #  species with sig first-order linear DBH term
n_spst_RW_DBH_2nd_order=26
n_spst_RW_DBH_2nd_order_neg=21
n_spst_BAI_DBH_best_model=42 #exception: ACRU at HF  
n_spst_BAI_DBH_best_model_pos=40 #exceptions: PIPO at LT (reconstructed DBH down to only 15cm) and PILO at CB (short DBH range on old trees), both neg but not significant
n_spst_BAI_DBH_best_model_2nd=41
n_spst_BAI_DBH_best_model_2nd_neg=40 # exception: PILO at CB
n_spst_dAGB_DBH_best_model=42 # exception: PILO at CB
```

@@

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Jan6)
n_tested=37 #same for all metrics
n_best_model_RW=30
n_best_model_BAI=31
n_best_model_AGB=30
n_best_model_neg_RW=n_best_model_RW-3 #(exceptions:  FASY at ZOF, PIPU and PIFL at CB)  90%
n_best_model_neg_BAI=n_best_model_BAI-3 #(exceptions:  FASY at ZOF, PIPU and PIFL at CB) 90.3%
n_best_model_neg_AGB=n_best_model_AGB-3 #(exceptions:  FASY at ZOF, PIPU and PIFL at CB) 90%
percent_sig_neg_trend_of_analyzed = n_best_model_neg_RW=n_best_model_RW/ n_tested*100
#species consistently independent of year: PIEN and PILO at CB, CHTA at HKK, PIST3 at NM,

@@

There was a significant effect of `year` in the GLS models for `r n_best_model_RW` - `r n_best_model_BAI` (depending on growth metric) of the `r n_tested` species- site combinations tested (Figs. `r year_fig`, `r all_GLS`), and these trends were consistent with those observed in a separate analysis of $DBH$-growth relationships by year (Appendix `r decadal_analysis_appendix`; [**ADD SI FIGS--issue 104**](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/104)).
In 90% of cases, the growth trend over time was negative.
Declines were particularly dramatic for *Picea mariana* at SC, *Pinus ponderosa* at LT, all four species at HF, and several species at SCBI  (Fig. `r year_fig`).
In these cases, models without `year` predicted declines in growth at large DBH that should more properly be attributed to the effect of year (Fig. `r year_fig`).
Significant positive growth trends were observed for only three species, *Fagus sylvatica* at ZOF, *Picea pungens* and *Pinus flexilis* at CB, and all were modest compared to the steep negative trends observed for some species.
Growth rate was consistently independent of `year` for only four species: *Chukrasia tabularis* at HKK, *Pinus strobiformis* at LT, and *Picea engelmannii* and *Pinus longaeva* at CB.

@@

It is notable that growth rates are changing directionally for the majority (`r percent_sig_neg_trend_of_analyzed`%) of site-species combinations that could be analyzed (Fig. `r year_fig`).

>>>>

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Jan12)
n_spst_DBH_analyzed= 43 # n species with DBH analyzed: 43 (45 - 2: 2 Hansley)
n_spst_RW_DBH_sig=35 #  species with sig first-order linear DBH term
n_spst_RW_DBH_2nd_order=26
n_spst_RW_DBH_2nd_order_neg=21
n_spst_BAI_DBH_best_model=42 #exception: ACRU at HF  
n_spst_BAI_DBH_best_model_pos=40 #exceptions: PIPO at LT (reconstructed DBH down to only 15cm) and PILO at CB (short DBH range on old trees), both neg but not significant
n_spst_BAI_DBH_best_model_2nd=41
n_spst_BAI_DBH_best_model_2nd_neg=40 # exception: PILO at CB
n_spst_dAGB_DBH_best_model=42 # exception: PILO at CB
```

@@

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Jan6)
n_tested=37 #same for all metrics
n_best_model_RW=30
n_best_model_BAI=32
n_best_model_AGB=30
n_best_model_neg_RW=n_best_model_RW-3 #(exceptions:  FASY at ZOF, PIPU and PIFL at CB)  90%
n_best_model_neg_BAI=n_best_model_BAI-3 #(exceptions:  FASY at ZOF, PIPU and PIFL at CB) 90.6%
n_best_model_neg_AGB=n_best_model_AGB-3 #(exceptions:  FASY at ZOF, PIPU and PIFL at CB) 90%
percent_neg_of_sig_trends="90-91%"
percent_sig_neg_trend_of_analyzed = "73-78%" 
#species consistently independent of year: PIEN and PILO at CB, CHTA at HKK, PIST3 at NM,

@@

There was a significant effect of `year` in the GLS models for `r n_best_model_RW` - `r n_best_model_BAI` (depending on growth metric) of the `r n_tested` species- site combinations tested (Figs. `r year_fig`, `r all_GLS`), and these trends were consistent with those observed in a separate analysis of $DBH$-growth relationships by year (Appendix `r decadal_analysis_appendix`; [**ADD SI FIGS--issue 104**](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/104)).
In `r percent_neg_of_sig_trends` of cases (depending on growth metric), the growth trend over time was negative.
Declines were particularly dramatic for *Picea mariana* at SC, *Pinus ponderosa* at LT, all four species at HF, and several species at SCBI  (Fig. `r year_fig`).
In these cases, models without `year` predicted declines in growth at large DBH that should more properly be attributed to the effect of year (Fig. `r year_fig`).
Significant positive growth trends were observed for only three species, *Fagus sylvatica* at ZOF, *Picea pungens* and *Pinus flexilis* at CB, and all were modest compared to the steep negative trends observed for some species.
Growth rate was consistently independent of `year` for only four species: *Chukrasia tabularis* at HKK, *Pinus strobiformis* at LT, and *Picea engelmannii* and *Pinus longaeva* at CB.

@@

It is notable that growth rates are changing directionally for the majority (`r percent_sig_neg_trend_of_analyzed`, depending on growth metric) of site-species combinations that could be analyzed (Fig. `r year_fig`).
